---
title: "Data Visualization Lab #1"
format:
  revealjs:
    embed-resources: true
lightbox: true
---

```{r}
#| label: setup
#| include: false

library(tidyverse)
library(palmerpenguins)
data(penguins)
```

---

How do I start making a graph using the `penguins` dataset?

::: {.fragment}
```{r}
#| eval: false
#| echo: true

ggplot(data = penguins)
```

:::

---

What `geom` layer would I use to make a graph of `body_mass_g` for all of the penguins in the dataset?

```{r}
#| eval: false
#| echo: true

ggplot(data = penguins) +
  _________(mapping = aes(x = body_mass_g))
```

---

What `geom` layer would I use to make a graph of `body_mass_g` for all of the penguins in the dataset?

```{r}
#| echo: true
#| code-line-numbers: "2"

ggplot(data = penguins) +
  geom_histogram(mapping = aes(x = body_mass_g)) +
  labs(
    title = "Distribution of Penguin Body Mass",
    x = "Body Mass (g)",
    y = "Count"
  ) +
  theme_minimal()
```

---

What `geom` layer would I use to make a graph of penguins by sex and species?

```{r}
#| eval: false
#| echo: true

ggplot(data = penguins) +
  _________(mapping = aes(x = species, fill = sex), position = "dodge")
```

---

Which function would I use to change the appearance of the x-axis?

```{r}
#| eval: false
#| echo: true
#| code-line-numbers: "2,3"

ggplot(data = penguins) +
  geom_bar(mapping = aes(x = species, fill = sex), position = "dodge") +
  ______x_discrete(labels = c("Adelie", "Chinstrap", "Gentoo"))
```

---

Which function would I use to change the appearance of the x-axis?

```{r}
#| echo: true
#| code-line-numbers: "3,4"

ggplot(data = penguins) +
  geom_bar(mapping = aes(x = species, fill = sex), position = "dodge") +
  scale_x_discrete(labels = c("Adelie", "Chinstrap", "Gentoo")) +
  scale_fill_discrete(labels = c("Female", "Male", "NA")) +
  labs(
    title = "Distribution of Penguin Body Mass",
    x = "Body Mass (g)",
    y = "Count"
  ) +
  theme_minimal()
```

---

What `geom` layer would I use to make a graph of bill length and bill depth?

```{r}
#| eval: false
#| echo: true

ggplot(data = penguins) +
  ________(mapping = aes(x = bill_length_mm, y = bill_depth_mm))
```

---

What `geom` layer would I use to make a graph of bill length and bill depth?
  
```{r}
#| echo: true
#| code-line-numbers: "2-7"

ggplot(data = penguins) +
  geom_point(mapping = aes(x = bill_length_mm, y = bill_depth_mm)) +
  geom_smooth(
    mapping = aes(x = bill_length_mm, y = bill_depth_mm),
    method = "lm",
    se = FALSE
  ) +
  labs(
    title = "Bill Length vs. Bill Depth",
    x = "Bill Length (mm)",
    y = "Bill Depth (mm)"
  ) +
  theme_minimal()
```

---

What `geom` layer would I use to make a graph of flipper length by species?

```{r}
#| eval: false
#| echo: true

ggplot(data = penguins) +
  ________(mapping = aes(x = sex, y = flipper_length_mm))
```

---

What `geom` layer would I use to make a graph of flipper length by sex?
  
```{r}
#| echo: true
#| code-line-numbers: "2"

ggplot(data = penguins) +
  geom_boxplot(mapping = aes(x = sex, y = flipper_length_mm)) +
  scale_x_discrete(labels = c("Female", "Male", "NA")) +
  labs(
    title = "Flipper Length by Sex",
    x = "Sex",
    y = "Flipper Length (mm)"
  ) +
  theme_minimal()
```

---

What is missing from this graph?
  
```{r}
#| echo: true

ggplot(data = penguins) +
  geom_boxplot(mapping = aes(x = sex, y = flipper_length_mm)) +
  scale_x_discrete(labels = c("Female", "Male", "NA")) +
  labs(
    title = "Flipper Length by Sex",
    x = "Sex",
    y = "Flipper Length (mm)"
  ) +
  theme_minimal()
```

---

What `geom` layer would I use to make a graph of flipper length by sex?
  
```{r}
#| echo: true
#| code-line-numbers: "8"

ggplot(data = penguins) +
  geom_boxplot(mapping = aes(x = sex, y = flipper_length_mm)) +
  scale_x_discrete(labels = c("Female", "Male", "NA")) +
  labs(
    title = "Flipper Length by Sex",
    x = "Sex",
    y = "Flipper Length (mm)",
    caption = "Source: palmerpenguins package"
  ) +
  theme_minimal()
```