---
title: "Assignment #8"
author: "SMPA 2152 (Prof. Bell)"
# format:
#   pdf:
#     mainfont: "Arial"
#     keep-tex: true
#     include-in-header:
#        text: |
format: gfm
execute:
  echo: true
  include: true
  warning: false
  message: false
editor_options: 
  chunk_output_type: inline
---

For this week's homework, we will use hypothesis tests and regression to explore Americans' views of free expression on college campuses. You will need to download the data for the [Ipsos/Knight Foundation Survey: Free Expression in America Post-2020](https://doi.org/10.25940/ROPER-31119146) from Roper iPoll.

```{r}
#| label: setup

library(tidyverse)
library(infer)
library(sjPlot)
poll <- read_csv("31119146.csv")
```

**BEFORE YOU BEGIN**: Make the following change to your data frame in your setup chunk before proceeding to any analysis.

```{r}
#| label: modify
#| include: true
#| echo: true

poll <- 
  poll |>
  mutate(Main_Weights = ifelse(!is.na(Students_Weights),
                               Students_Weights,
                               Main_Weights))
```

1. Conduct a hypothesis test showing whether the proportion of college students who believe that colleges and universities should **allow** offensive political speech on campus is less than among non-college students (`Q11_4`). You must write both the $H_0$ and the $H_A$. How do you interpret the results of your hypothesis test?

    Please note that **non**-college students are represented with the values `No` *and* `NA` in the variable `Student1`; any other values represent college students. You should have 4,186 non-college students and 996 college students.

```{r}
#| label: hypotheses
#| output: asis
#| echo: false

writeLines(c("* $H_0$: The proportion of college students who believe that colleges and universities should allow offensive political speech is greater than or equal to the proportion among non-college students.", "* $H_A$: The proportion of college students who believe that colleges and universities should allow offensive political speech is less than the proportion among non-college students."), sep = "\n")
```

```{r}
#| label: hypothesis_test

poll |>
  filter(Q11_4 != "Skipped") |>
  mutate(College = ifelse(Student1 == "No" | is.na(Student1), "Not a student", "Student"),
         College = factor(College, levels = c("Not a student", "Student")),
         AllowSpeech = ifelse(Q11_4 == "Allow", 1, 0)) |>
  t_test(AllowSpeech ~ College,
         order = c("Student", "Not a student"),
         alternative = "less") |>
  knitr::kable()
```

```{r}
#| label: hypothesis_test_result
#| output: asis
#| echo: false

writeLines("> The p-value is .013, so we can reject $H_0$ and accept $H_A$, which is that non-college students are 3.8 percentage points less likely to support allowing offensive political speech on campus, on average.")
```

2. Using a linear probability model, estimate the difference in proportions from \#1 incorporating the survey weights. How does the estimated difference change when using survey weights?

```{r}
#| label: simple_regression

poll2 <- poll |>
  filter(Q11_4 != "Skipped") |>
  mutate(College = ifelse(Student1 == "No" | is.na(Student1), "Not a student", "Student"),
         College = factor(College, levels = c("Not a student", "Student")),
         AllowSpeech = ifelse(Q11_4 == "Allow", 1, 0))

reg <- lm(AllowSpeech ~ College, weight = Main_Weights, data = poll2)
tab_model(reg,
          prefix.labels = "label",
          show.reflvl = TRUE,
          show.ci = FALSE,
          dv.labels = "Allow Offensive Speech on Campus")
```

```{r}
#| label: simple_regression_result
#| output: asis
#| echo: false

writeLines("> With weights, college students are 7 percentage points less likely to support allowing offensive political speech on campus, on average, which is about twice as large the estimate from the t-test.")
```

3. Include at least two confounders in the regression you conducted for \#3. Please explain why you chose to control for those confounders (i.e., why do you think that variable is a confounder? Remember that confounders must explain change in both the dependent and the independent variables.)

    In addition, please describe the effect of being a current college student on support for allowing offensive political speech on campus given your results.

    Some potential confounders include:

    * Party ID: `QPID100`
    * Gender: `ppgender`
    * Household income: `ppinc7`
    * Race/Ethnicity: `ppethm`
    
```{r}
#| label: multiple_linear_regression

poll3 <- poll |>
  filter(Q11_4 != "Skipped" & QPID100 != "Skipped") |>
  mutate(College = ifelse(Student1 == "No" | is.na(Student1), "Not a student", "Student"),
         College = factor(College, levels = c("Not a student", "Student")),
         AllowSpeech = ifelse(Q11_4 == "Allow", 1, 0),
         QPID100 = ifelse(QPID100 == "Something else", "Independent", QPID100),
         QPID100 = factor(QPID100, levels = c("Independent", "Democrat", "Republican")))

reg <- lm(AllowSpeech ~ College + QPID100 + ppgender, weight = Main_Weights, data = poll3)
tab_model(reg,
          prefix.labels = "label",
          show.reflvl = TRUE,
          show.ci = FALSE,
          dv.labels = "Allow Offensive Speech on Campus")
```

```{r}
#| label: reg_result
#| output: asis
#| echo: false

writeLines("> College students are about 6 percentage points less likely to support allowing offensive political speech on campus, on average, controlling for gender and political party.")
```