---
title: "Assignment #5"
author: "SMPA 2152 (Prof. Bell)"
# format:
#   pdf:
#     mainfont: "Arial"
#     keep-tex: true
#     include-in-header:
#        text: |
format: gfm
execute:
  echo: true
  include: true
  warning: false
  message: false
editor_options: 
  chunk_output_type: inline
---
\vspace{-3em}

For this week's homework, we are going to explore how well the polls did in predicting the results of the 2020 Presidential Election. We will be using two datasets:

- Data on 2020 election polls collected by [FiveThirtyEight](https://abcnews.go.com/538). This data is available on Blackboard as `presidential_polls_2020.csv`.

- Results of the 2020 Presidential election compiled by the [MIT Election Data + Science Lab](https://electionlab.mit.edu/). This data is available on Blackboard as `2020-president.csv`.
    
---

```{r}
#| label: setup

library(tidyverse)
polls <- read_csv("presidential_polls_2020.csv")
```

1. Make a nicely-formatted graph showing the average support for Joe Biden and Donald Trump in each month over the course of the race. 

    1. Use the column `end_date` to represent the date of the poll.
    2. Use only polls that are national polls (i.e., are not state polls).
    3. Use only pollsters with a rating from 538 of 2.0 or higher.
    
```{r}
polls |>
  filter(answer %in% c("Biden", "Trump") & numeric_grade >= 2 & !is.na(state)) |>
  mutate(end_date = mdy(end_date),
         month = month(end_date),
         year = year(end_date)) |>
  group_by(answer, month, year) |>
  summarize(pct = mean(pct, na.rm = T)) |>
  mutate(date = make_date(year, month)) |>
  ggplot(aes(x = date, y = pct, color = answer)) +
  geom_point() +
  geom_line() +
  scale_x_date(date_breaks = "2 months", date_labels = "%b %y") +
  scale_y_continuous(limits = c(0,100)) +
  labs(x = "Month",
       y = "Polling Average (%)",
       color = "Candidate",
       title = "2024 Presidential Election National Polling",
       caption = "Source: 538 and MIT Election Data + Science Lab.") +
  theme_classic() +
  theme(plot.title = element_text(hjust = .5))
```

2. Some people believe that polls with live interviews produce more accurate results than other types of polls. Create the same graph as above, but this time, include a comparison between polls that use at least some `"Live Phone"` interviews and those that do not. Do you believe that Live Phone polls produce different polling results than non-Live Phone polls?

```{r}
polls |>
  filter(answer %in% c("Biden", "Trump") & numeric_grade >= 2 & !is.na(state)) |>
  pivot_wider(names_from = answer, values_from = pct) |>
  separate_wider_delim(end_date, "/", names = c("month", "day", "year")) |>
  mutate(live = str_detect(methodology, "Live Phone")) |>
  group_by(month, year, live) |>
  summarize(Biden = mean(Biden, na.rm = T),
            Trump = mean(Trump, na.rm = T)) |>
  mutate(date = str_c(year, month, sep = "-"),
         date = ym(date)) |>
  pivot_longer(c(Biden, Trump), names_to = "candidate", values_to = "pct") |>
  ggplot(aes(x = date, y = pct, color = candidate)) +
  geom_point() +
  geom_line() +
  scale_x_date(date_breaks = "2 months", date_labels = "%b %y") +
  scale_y_continuous(limits = c(0,100)) +
  labs(x = "Month",
       y = "Polling Average (%)",
       color = "Candidate",
       title = "2024 Presidential Election National Polling",
       caption = "Source: 538 and MIT Election Data + Science Lab.") +
  theme_classic(base_size = 8) +
  theme(plot.title = element_text(hjust = .5)) +
  facet_wrap(~ live)
```

```{r}
#| output: asis
#| echo: false

writeLines("> Polls with live phone interviews were better at capturing late movement towards Trump than non-live phone interview polls.")
```

3. Estimate the polling error in each state by comparing the average two-party vote share for Biden in each state according to the polling vs. the actual two-party vote share for Biden in the election results. The two party vote share is:

    $BidenPct/(BidenPct + TrumpPct)$
    
    Use only polls where:

    1. The `end_date` is on or after October 15, 2020.
    2. The pollster has a rating from 538 of 2.0 or higher.

Make a nicely-formatted graph showing the polling error in each state arranged from largest to smallest polling error. Comment on the graph. What does this graph tell you about state polling in the 2020 election?

```{r}
elec <- read_csv("2020-president.csv")
elec <- elec |>
  filter(candidate_name == "Biden") |>
  mutate(two_party_vote = two_party_vote*100)

polls |>
  mutate(date = mdy(end_date)) |>
  filter(answer %in% c("Biden", "Trump") &
           numeric_grade >= 2 &
           date >= mdy("10-15-2020") &
           !is.na(state)) |>
  pivot_wider(names_from = answer, values_from = pct) |>
  mutate(BidenShare = Biden/(Biden+Trump)*100,
         state = str_to_upper(state)) |>
  group_by(state) |>
  summarize(BidenTwoParty = mean(BidenShare, na.rm = T)) |>
  inner_join(elec) |>
  mutate(difference = BidenTwoParty - two_party_vote,
         state = str_to_title(state),
         state = fct(state),
         state = fct_reorder(state, difference)) |>
  ggplot() +
  geom_col(aes(y = state, x = difference)) +
  labs(x = "Polling Error (%)",
       y = "State",
       title = "Polling Error in the 2024 Presidential Election",
       caption = "Source: 538 and MIT Election Data + Science Lab.") +
  theme_classic(base_size = 8) +
  theme(plot.title = element_text(hjust = .5))
```

```{r}
#| output: asis
#| echo: false

writeLines("> Some of the largest polling errors were in states that are not competitive, meaning that there probably was not much polling in those states. However, most states have a polling error which overestimates Biden's vote share, suggesting a general pattern in 2020 election polling to overestimate Biden.")
```