---
title: "Assignment #1"
author: "SMPA 2152 (Prof. Bell)"
# format:
#   pdf:
#     mainfont: "Arial"
#     keep-tex: true
#     include-in-header:
#        text: |
#          \usepackage{fvextra}
#          \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines=true, breakanywhere=true, breaksymbol=, breakanywheresymbolpre=,commandchars=\\\{\}}
#          \DefineVerbatimEnvironment{OutputCode}{Verbatim}{breaklines=true, breakanywhere=true, breaksymbol=, breakanywheresymbolpre=,commandchars=\\\{\}}
format: gfm
execute:
  echo: true
  include: true
  warning: false
  message: false
editor_options: 
  chunk_output_type: console
---
\vspace{-3em}

For this homework, please use the `assignment1_template.R` script. Please submit your completed `.R` script via Blackboard. In addition, please submit a Word document or PDF containing the visualizations for questions 5 and 6.

**To save a graph and download it to your computer in Posit Cloud:**

1. In the "Plots" pane, select "Export" and then "Save as Image."
2. Give the file a name and use the drag button in the corner of the graph to resize the image to proper dimensions. Click "Save."
3. In the "Files" pane, select the check mark next to your `.png` file. Click "More", and then "Export..." Click "Download" to download the file to your computer.

    If you select the check mark next to multiple files, you will export a .zip folder. Before submitting any work in this class, you must unzip the folder to obtain the unzipped files. Do not submit a zip folder for an assignment.

You may complete the assignments on your own or in collaboration with other students. This means that you may work together to write code and/or solve problems. **Do not split up the questions or combine independent work.**

If you work with other students, please indicate their names at the top of your submission. Each student must submit an assignment on Blackboard.
\vspace{-1em}

---

1. Install the `{nycflights13}` package and load the `flights` data frame.

```{r}
# Install the "nycflights13" package. I have this line commented out because I only need to install the package once.
# install.packages("nycflights13")
library(nycflights13)
data(flights)
```

2. Explore the data frame using `glimpse()`. (Remember to load the `{dplyr}` package first.) If we wanted to calculate the departure delay, can we subtract `dep_time` from `sched_dep_time`? Why or why not?

```{r}
library(dplyr)
glimpse(flights)
```

```{r}
flights$new_dep_delay <- flights$dep_time - flights$sched_dep_time
identical(flights$new_dep_delay, flights$dep_delay)
```

```{r}
#| output: asis
#| echo: false

writeLines("> `dep_time` and `sched_dep_time` are integers, not times (e.g., `600-557` is `43`, not `3` minutes).")
```

3. Now we want to find out how many flights were delayed by 30 minutes or more when departing JFK airport. First, create a new data frame with only those rows where the origin airport is "JFK" and where the departure delay is greater than or equal to 30. Then, use the `nrow()` function to get the number of rows in the resulting data frame.

```{r}
jfk_delays <- flights[flights$origin == "JFK" & flights$dep_delay >= 30,]
nrow(jfk_delays)
```

4. In your new data frame, create a new column that represents the departure delay in hours rather than minutes (i.e., divide departure delay by 60). What is the average departure delay of these flights in hours? Hint: look at the help file for `mean()`. How can you ask this function to ignore the flights where the departure delay is `NA` (because the flight was cancelled)?

```{r}
jfk_delays$dep_delay_hours <- jfk_delays$dep_delay/60
mean(jfk_delays$dep_delay_hours, na.rm = TRUE)
```

5. Create a histogram showing the departure delays from JFK airport in hours. Each bar should represent 20 minutes (i.e., 1/3 of an hour). Your graph should include a theme, a title, proper axis labels, and a caption.

```{r}
library(ggplot2)
ggplot(data = jfk_delays) +
  geom_histogram(mapping = aes(x = dep_delay_hours), binwidth = .33) +
  theme_classic() +
  labs(x = "Departure Delay (hours)",
       y = "Count",
       title = "JFK Departure Delays",
       caption = "Source: {nycflights13} package.") +
  theme(plot.title = element_text(hjust = .5))
```

6. Let's return to the original `flights` data frame now. Limit the data frame to only the three major airlines (`AA` for American Airlines, `DL` for Delta Airlines, and `UA` for United Airlines). Create a bar graph showing how many flights each airline took from each of the three NYC airports (JFK, LGA, and EWR). Your graph should include a theme, a title, proper axis labels, and a caption.

```{r}
ggplot(data = flights[flights$carrier %in% c("AA", "DL", "UA"),]) +
  geom_bar(mapping = aes(x = origin, fill = carrier), position = "dodge") +
  theme_classic() +
  labs(x = "Airport",
       y = "Count",
       fill = "Airline",
       title = "Which Major Airlines Fly from NYC Airports?",
       caption = "Source: {nycflights13} package.") +
  theme(plot.title = element_text(hjust = .5))
```