---
title: "Assignment #1"
author: "SMPA 2152 (Prof. Bell)"
# format:
#   pdf:
#     mainfont: "Arial"
#     keep-tex: true
#     include-in-header: 
#        text: |
#          \usepackage{fvextra}
#          \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines=true, breakanywhere=true, breaksymbol=, breakanywheresymbolpre=,commandchars=\\\{\}}
#          \DefineVerbatimEnvironment{OutputCode}{Verbatim}{breaklines=true, breakanywhere=true, breaksymbol=, breakanywheresymbolpre=,commandchars=\\\{\}}
format: gfm
execute:
  echo: true
  include: true
  warning: false
  message: false
editor_options: 
  chunk_output_type: console
---
\vspace{-3em}

For this homework, please use the "assignment1_template.R" script.

You may complete the assignments on your own or in collaboration with other students. This means that you may work together to write code and/or solve problems. **Do not split up the questions or combine independent work.**

If you work with other students, please indicate their names at the top of your submission. Each student must submit an assignment on Blackboard.
\vspace{-1em}

---

1. Install the `{nycflights13}` package and load the `flights` data frame.

```{r}
# Install the "nycflights13" package. I have this line commented out because I only need to install the package once.
# install.packages("nycflights13")
library(nycflights13)
data(flights)
```

2. Explore the data frame using `glimpse()`. (Remember to load the `{dplyr}` package first.) If we wanted to calculate the departure delay, can we subtract `dep_time` from `sched_dep_time`? Why or why not?

```{r}
library(dplyr)
glimpse(flights)
```

```{r}
flights$new_dep_delay <- flights$dep_time - flights$sched_dep_time
identical(flights$new_dep_delay, flights$dep_delay)
```

```{r}
#| output: asis
#| echo: false

cat("`dep_time` and `sched_dep_time` are integers, not times (e.g., `600-557` is `43`, not `3` minutes).")
```

3. Now we want to find out how many flights were delayed by 30 minutes or more when departing JFK airport. First, create a new data frame with only those rows where the origin airport is "JFK" and where the departure delay is greater than or equal to 30. Then, use the `nrow()` function to get the number of rows in the resulting data frame.

```{r}
jfk_delays <- flights[flights$origin == "JFK" & flights$dep_delay >= 30,]
nrow(jfk_delays)
```

4. In your new data frame, create a new column that represents the departure delay in hours rather than minutes (i.e., divide departure delay by 60). What is the average departure delay of these flights in hours? Hint: look at the help file for `mean()`. How can you ask this function to ignore the flights where the departure delay is `NA` (because the flight was cancelled)?

```{r}
jfk_delays$dep_delay_hours <- jfk_delays$dep_delay/60
mean(jfk_delays$dep_delay_hours, na.rm = TRUE)
```

